\bf On semidefinite-representable sets over valuation fields

### 2025-05-15 article/paper_padic_spec.tex
stat prop 3.11

\begin{remark}
The valuation $\val$ is discrete. Thus if \eqref{LP} admits feasible vectors, $p^*$ is either $- \infty$ or reached by a certain solution $x^*$.
\end{remark}

In this section we present an algorithm for solving \eqref{LP} which starts by eliminating the constraint forced by $D$ and $e$ by operating a substitution. Then it reduces the matrix $A$ to
Smith Normal Form, thus reducing a general linear program to a diagonal linear program. The latter problem being easily solved by simple calulations in $K$.

The first proposition we prove  allows to consider only iterations of~\eqref{LP} with data of the form $(A,b,c,0,0)$.

\begin{proposition}\label{reducD}
  Let $A \in \allmat_{d,n}(K), b \in K^d, c\in K^n$, $D \in \allmat_{m,n}$, $e \in K^m$ and let $J \in \allmat_{n,R}\left( K \right) $ be a matrix such that ${\rm Im } J = \ker D$ where $R$ denotes the dimension of $\ker D$. 
  Additionally, we assume the existence of $x_0 \in K^n$ that verifies $D x_0 =e$ as if
  there are no such vector the problem~\ref{LP} with data $(A,b,c,D,e)$ is not solvable.

  Let $x \in \{x \in K^n : Dx=e\} = x_0 + \ker D $ and let $y \in K^R$ denote the unique element of
  $K^n$ such that $x = x_0 + J y$, then :
  \begin{enumerate}
    \item\label{reducD_item1} $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
      $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$.
    \item\label{reducD_item2} $x$ is a solution for~\eqref{LP} with data $(A,b,c,D)$ if and only if 
      $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$ and $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$.
  \end{enumerate}
\end{proposition}

>>>>

\begin{remark}
  Assume $\val$ is a discrete valuation. Then if \eqref{LP} admits feasible vectors,
  $p^*$ is either $-\infty$ or attained at some solution $x^*$.
\end{remark}

In this section we present an algorithm for solving \eqref{LP} which starts by
eliminating the equality constraint defined by $D$ and $e$ by operating a substitution.
Then the algorithm reduces the matrix $A$ to Smith Normal Form, thus reducing a general
linear program to a diagonal linear program. The reduced problem is then easily solved
by simple calulations in $K$\footnote{\simone{changer formulation}}.

The first result allows us to consider only iterations of~\eqref{LP} with data of the
form $(A,b,c,0,0)$. When $Dx=e$ has no solution, \eqref{LP} is infeasible, thus
we only consider the case when $Dx=e$ has a solution.

\begin{proposition}\label{reducD}
  Let $A \in K^{d \times n}, b \in K^d, c\in K^n$, $D \in K^{m\times n}$,
  $e \in K^m$ and let $J \in K^{n \times R}$ be a matrix such that
  ${\rm Im}\, J = \ker D$ and $R = \dim \ker D$.
  Assume there exists $x_0 \in K^n$ such that $D x_0 = e$, and let
  $x \in \{z \in K^n : Dz = e\} = x_0 + \ker D$.
  Let $y \in K^R$ denote the unique element of $K^n$ such that
  $x = x_0 + J y$. Then:
  \begin{enumerate}
  \item\label{reducD_item1}
    $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
    $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$.
  \item\label{reducD_item2}
    $x$ is a solution for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
    $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$ and
    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$.
  \end{enumerate}
\end{proposition}
